Link Parses to Directed Acyclic Graphs

### 2014-05-12 doc/LinksToDAG.tex
merged trials.sh

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

@@

\author{Juneki Hong \\
  Department of Computer Science \\
  Johns Hopkins University \\
  Baltimore, MD 21218, USA \\ 
  {\tt juneki@cs.jhu.edu} \\\And
  Jason Eisner \\
  Department of Computer Science \\
  Johns Hopkins University \\
  Baltimore, MD 21218, USA \\
  {\tt jason@cs.jhu.edu} \\
}

@@

\bibliographystyle{acl}
\bibliography{LinksToDAG}

>>>>

\documentclass[11pt]{article}
\usepackage{LinksToDAG}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

@@

\author{Juneki Hong and Jason Eisner\\
  Department of Computer Science \\
  Johns Hopkins University \\
  Baltimore, MD 21218, USA \\ 
  {\tt \{juneki,jason\}@cs.jhu.edu} \\
}

@@

\section{ILP Encoding}
We ignored the link parses that the link parser could not find suitable attachments and returned a disconnected graph.

\section{Conll-Link analysis}

\bibliographystyle{LinksToDAG}
\bibliography{LinksToDAG}
